Insight Into Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-09-12 draft.tex
Revised Bernhard done

Pinhero et al. applied association rule mining to create high-confidence decision rules based on variables such as age, gender and geographic location about the mortality rate in liver cancer data \cite{Pinheiro}.
%%
Sekhavat and Hoeber propose an interactive visualization technique for decision trees, where all decisions are displayed in a heat map \cite{Sekhavat}.
%%
The visualization translates the decision tree into a heat map, where each cell represents the connectivity between an initial value and an target value.
%%
The resulting interactive visualization is well suited for analyzing single, but not multiple decision trees.
%%
\paragraph{SHIP Data Analysis.}
Klemm et al. analyzed the lumbar spine variability of of 490 \texttt{SHIP-2} subjects \cite{Klemm2013VMV}.
%%
They incorporate hierarchical agglomerative clustering to derive shape groups, yielding several groups of average shape and several outlier cluster.
%%
The extracted lumbar spine shape was correlated with subject size.
%%
Our data extraction process is based on the detection algorithm and lumbar spine canal extraction presented by \cite{Klemm2013VMV}.
%%
Clustering techniques applied to non-image data are strongly dependent on the chosen variables and distance measures.
%%
%Klemm et al. found \texttt{k-Prototypes} and \texttt{DBSCAN} appropriate for this task \cite{Klemm2014BVM}.
%%
\\\\
Unique for our work is the combination of data mining techniques with an IVA-approach by observing interesting feature relations in context of image-derived features using multiple decision trees for one visualization.
%%
We abstract the decision tree results similar to \cite{Turkay}, making them comparable in an overview visualization.
%%
\section{The Lumbar Spine Data Set}
\label{sec:MaterialsAndMethod}
%%
\noindent Our approach allows to analyze many variables simultaneously.
%%
Therefore, epidemiologists compiled the data set with a with a wide range of variables possibly correlating with lumbar back pain.
%%
The data set comprises of 6.753 subjects from two cohorts (4.420 from \texttt{SHIP-Trend-0} and 2.333 from \texttt{SHIP-2}).
%%
%It is an active research area to determine these correlations.
%%

@@

\subsection{Interactive Display of Decision Trees}
We have to create a decision tree for every non-image variable to analyze which one can be explained by image-derived variables.
%%
Since we have 134 non-image variables, the calculation yields a corresponding number of trees.
%%
Further subdivision, e.g. by quantiles of \emph{body size} increases the number to 402 trees.
%Dividing the subjects into four groups using body size, the number increases to 402 trees.
%%
%To make the results cognitive feasible, we have to abstract the results of the classification.
We have to abstract the results of the classification to keep the mental effort of interpreting the data low.
%%------------
\subsubsection{Visualization of Classification Results}
\label{subsec:VisualizationOfClassificationResults}
%%
%We follow the visual information-seeking mantra and want to provide an overview first, then details-on-demand \cite{shneiderman1996}.
We follow the Visual Analytics mantra by analyzing first, show the important and analyze further \cite{Keim}.
%%
A first analysis step was performed by applying the classification algorithm to the data.
%%
The optimal classification uses a few rules to precisely characterize the target variable.
%%
Therefore, we are interested in \emph{small trees} with a \emph{low classification error rate}.
%%
The two measures form the axis for a \emph{scatter plot} of the classification results.

\paragraph{The Error Term. }
Normally the error rate for a classification is calculated with $error = \frac{classifiedCorrectly_{n}} {n}$ where $n$ is the number of subjects.
%%
The metric usually works well for variables with uniform distribution.
%%
It distorts the result for other distribution types.
%%
If for example a variable indicating a disease is negative for 90\% of the subjects and the classifier simply assigns all subjects to \emph{not ill} the error metric would yield an error of 10\%, even though it is very bad.
%%
Our error term therefore incorporates the discriminative power of each manifestation and is denoted as follows:
%%
%Therefore the discriminative power of each dimension in the equation
%error = 1 - \frac{\[ \sum_{m=0}^M \] \frac{M_{classifiedCorrectly}}{M_all}}{number of dimensions}
\begin{equation}
error = 1 - \frac{\sum_{m=0}^M \frac{classifiedCorrectly_{m}}{all_{m}}}{number_{dimensions}}
\end{equation}
$M$ represents the set of manifestation of each variable.
%%
The error is scaled to denote perfect classification with 0 and 1 is equal to random selection.
% The error rate has to be judged depending on the number of classes of the target variable.
% %%
% An error rate of 50\% for a target variable with two manifestations makes the classifier equal to throwing a coin.
% %%
% The same error rate is acceptable a target variable with more than two manifestations.
% %%
% Picking a value for a variable of four manifestations with an error rate of 50\% is better than the random selection (error rate of 75\%).
% %%
% The following scales the error rate so that 0 denotes perfect classification and 1 is equal to random selection.
% %%
% \begin{equation}
% error_{normalized} = \frac{error}{100 - \frac{100}{class number}}
% \end{equation}
%%
%%
We consider a result rated below $0.25$ a good classification.
%%
It allows for comparability of error rates between variables with different manifestation count.

@@

The x-axis shows the number of decisions of the underlying model, the y-axis the classification error rate (see Section~\ref{subsec:VisualizationOfClassificationResults}).

@@

We only display variables with an error rate below $0.5$, results above this threshold are inaccurate.

@@

\subsubsection{All Variables}
%%
The vast majority of parameters can not be described well using the classifier.
%%
This is reflected in the large amount of variables classified with an error rate above $0.6$.
%%
%The first impression of the resulting scatter plots quickly shows a very high amount of variables above an error rate of $0.6$.
%%

% None of the pain indicators can be reliably described using the image-based parameter.
None of the pain indicators can be described reliably using the image-based parameters.
%%
The only variable reliably classified in this group is gender. % with an error rate of 31.5\% using a decision tree of seven rules.
%
It can be discriminated with an error rate of $0.31$ using 7 rules and incorporates only curvature and curvature angle variables.
%%
The distinctness lies in the average difference in body size between male and female subjects.
%
%It mostly incorporates \emph{mean curvature}, \emph{sagittal curvature angle} und sagittal \emph{mean curvature}.
%The perfect categorization of the \emph{dialysis} parameter was conspicuous.
%%
%This is due to the subject distribution among the manifestation.
%%
%Only two subjects receive a dialysis.
%%
%The good discrimination is not meaningful.
%%
\emph{Medication for high blood pressure} is classified for 1,058 subjects with an error rate of $0.47$ solely based on coronal mean curvature.
%%
%1,058 subjects are classified with an error rate of $0,47$ solely based on coronal mean curvature.
%%
Almost all subjects who are medicated ($796/1,058$) were correctly classified, the vast majority of non-medicated subjects ($262/1,058$) are false-positive classified.
%%
Therefore the classifier is not as useful.
%%This is however due to the high amount of people, who are medicated (68\%) and who are almost all correctly class
%%
%Other features well classified include marital status, foot pain and number of born children.
%%
The four body size groups could be characterized with an error rate $0.48$, but the decision tree comprises 71 rules and imposes overfitting.

The analysis of the dummy variable yields similar results like the \emph{blood pressure medication}.
%%
Variables, such as subjects sized 139-164 cm, between 64 and 90 years of age or nutrition related parameters are dominantly populated by one manifestation.
%%
The classifier neglects the other group and yields a error rate below $0.5$.
%The dummy variable analysis yields fewer results.
%%
%It shows that subjects between 64 and 90 years of age can be detected with 23\% error rate by using the curvature angle and coronal mean curvature.
%%
%Subjects with body size between 177 cm and 202 cm can classified with an error rate of 22,1\%. solely using mean curvature.
%%
\subsubsection{Gender Groups}
%%
Classification using groups divided by gender do not produce satisfying results.
%%
Only \emph{hypothyroidism} could be described for male subjects with an error rate of $0.24$ for 110 subjects using the \emph{mean curvature} and \emph{curvature angle}.
%%
Since there are only 30 male subjects diagnosed with \emph{hypothyroidism}, the statistical power of the result is reduced.
%%
The dummy variable analysis showed that female subjects of \emph{139-164~cm body size} could be discriminated using the \emph{mean curvature} and \emph{curvature angle}, with an error of $0.38$.

%\com{Potentially skip these due to the confounding of body size}
\subsubsection{Body-Mass-Index Groups}
%%
Gender could be classified for each \emph{BMI} group using \emph{mean curvature} and \emph{curvature angle}.
%%
The accuracy varies between $0.31$ (\emph{BMI} of \emph{$30.5-48$}, 4 decision rules) to $0.39$ (\emph{BMI} of \emph{$24.7-27.4$}, 5 decision rules).
%%
The starting age of smoking could be characterized well with an error rate between $0.25$ to $0.32$ for all \emph{BMI} groups except of subjects with BMI of \emph{$30.5-48$}.
%%
The result however is probably over fitted to the data due to tree sizes between $14$ and $16$.
%%
\com{Warum?}
%%

Some variables, such as \emph{body size} can be described with an error rate of $0.3$ to $0.36$ but only using large decision trees with over 20 rules.
%%
Notable is also the increasing accuracy with increasing decision tree size.
%%
Using mostly \emph{mean curvature} and \emph{curvature angle}, the leg pain level can be predicted using $14$ rules with an error rate of $0.46$ for obese subjects (\emph{BMI} higher than $30$).
%%
The dichotomous variable whether the subject has felt pain in the last seven days can also be predicted for this group using the same features.
%%
The resulting tree consists of $8$ rules and has an error of $0.35$.
%%
Obese subjects are prone to back and leg pain due to a more stressed lumbar spine.
%%
How much the spine is deformed under the heavy stress seems to directly influence the pain levels for these subjects.

The dummy variable analysis shows many results using a decision tree with one rule based on \emph{mean curvature} or \emph{curvature angle} with accuracy between $0.35$ and $0.47$.
%%
%It shows that mean curvature can be used to predict dependencies to variables, such as \emph{high blood pressure}, \emph{hypothyroidism} or \emph{nutrition}.

@@

\subsubsection{Size Groups}
%%
Many previously described results are confounded with subject size.
%%
Differences between \emph{male} and \emph{female} subjects are explained by to the average \emph{body size} difference.
%%
For example, large subjects are already characterized by their rather straight spine.
%
The question is, whether the inter-group spine-variability parameter is enough for predicting other parameter or not.
%%
Dividing subjects into \emph{body size} groups potentially highlights classifications not confounded by \emph{body size}.
%%
\paragraph{Large Decision Trees. }
Back pain-associated variables can be explained for various \emph{size}-groups, but we could not extract universal rules.
%%
Radiating back pain could be described with error rate of $0.39$ using 23 rules for subjects between \emph{$171-177~cm$ body size} using \emph{torsion} and \emph{mean curvature}.
%%
For subjects sized \emph{$177-202~cm$} the accuracy drops to $0.47$ using 20 decision rules.
%%
There are several decision trees for laboratory values, such as \emph{alanine aminotransferase} value (relevant for diagnosis of liver or gallbladder illness) in the blood can be described with an error rate of $0.4$ (\emph{$139-164~cm$}) to $0.36$ (\emph{$164 - 171~cm$}).
%%
Similar values can be observed for \emph{cholesterol} or \emph{age}.
%%
Due to the large decision trees, these results are not usable and impose overfitting to the data.
%%
\paragraph{Small Decision Trees. }
%%
The dummy variables show several variables described using only one decision rule with accuracy between $0.42$ to $0.47$.
%%
Most of these variables have a dominant manifestation and the classifier shows a low detection precision for the second manifestation.
%%
These variables include \emph{nutrition} parameter, \emph{thyroid disorder} and \emph{social problems induced by back pain}.

@@

Subjects grouped using \underline{body size} have a similar spine shape and a lower variance.
%%
The remaining information within these groups is not enough to characterize back pain-related variables.
%%
%Certain parameters can be classified in 
For some \emph{body size} groups, certain \emph{nutrition} or \emph{psychological} parameters can be predicted with a comparatively high error rate.
%Certain subgroups, however, can be classified for various size groups, such as nutrition or psychological parameters.
%%

@@

\section*{\uppercase{Acknowledgements}}

\noindent SHIP is part of the Community Medicine Research net of the University of Greifswald, Germany, which is funded by the Federal Ministry of Education and Research (grant no. 03ZIK012), the Ministry of Cultural Affairs as well as the Social Ministry of the Federal State of Mecklenburg-West Pomerania. Whole-body MR imaging was supported by a joint grant from Siemens Healthcare, Erlangen, Germany and the Federal State of Mecklenburg-Vorpommern. The University of Greifswald is a member of the ‘Centre of Knowledge Interchange’ program of the Siemens AG. This work was supported by the DFG Priority Program 1335: Scalable Visual Analytics.

>>>>

Pinhero et al. applied association rule mining to create high-confidence decision rules based on variables, such as age, gender and geographic location about the mortality rate in liver cancer data \cite{Pinheiro}.
%%
Sekhavat and Hoeber propose an interactive visualization technique for decision trees, where all decisions are displayed in a heat map \cite{Sekhavat}.
%%
The visualization translates the decision tree into a heat map, where each cell represents the connectivity between an initial value and an target value.
%%
The resulting interactive visualization is well suited for analyzing single, but not multiple decision trees.
%%
\paragraph{SHIP Data Analysis.}
Klemm et al. analyzed the lumbar spine variability of of 490 \texttt{SHIP-2} subjects \cite{Klemm2013VMV}.
%%
They incorporate hierarchical agglomerative clustering to derive shape groups, yielding several groups of average shape and several outlier cluster.
%%
The extracted lumbar spine shape was correlated with subject size.
%%
Our data extraction process is based on the detection algorithm and lumbar spine canal extraction presented by \cite{Klemm2013VMV}.
%%
Clustering techniques applied to non-image data are strongly dependent on the chosen variables and distance measures.
%%
%Klemm et al. found \texttt{k-Prototypes} and \texttt{DBSCAN} appropriate for this task \cite{Klemm2014BVM}.
%%
\\\\
Unique for our work is the combination of data mining techniques with an IVA-approach by observing interesting feature relations in context of image-derived features using multiple decision trees for one visualization.
%%
We abstract the decision tree results similar to \cite{Turkay}, making them comparable in an overview visualization.
%%
\section{The Lumbar Spine Data Set}
\label{sec:MaterialsAndMethod}
%%
\noindent Our approach allows to analyze many variables simultaneously.
%%
Therefore, epidemiologists compiled the data set with a with a wide range of variables possibly correlating with lumbar back pain.
%%
The data set comprises of 6.753 subjects from two cohorts (4.420 from \texttt{SHIP-Trend-0} and 2.333 from \texttt{SHIP-2}).
%%
%It is an active research area to determine these correlations.
%%

@@

\subsection{Interactive Display of Decision Trees}
We have to create a decision tree for every non-image variable to analyze which one can be explained by image-derived variables.
%%
Since we have 134 non-image variables, the calculation yields a corresponding number of trees.
%%
Further subdivision, e.g. by quantiles of \emph{body size} increases the number to 402 trees.
%Dividing the subjects into four groups using body size, the number increases to 402 trees.
%%
%To make the results cognitive feasible, we have to abstract the results of the classification.
We have to abstract the results of the classification to keep the mental effort of interpreting the data low.
%%------------
\subsubsection{Visualization of Classification Results}
\label{subsec:VisualizationOfClassificationResults}
%%
%We follow the visual information-seeking mantra and want to provide an overview first, then details-on-demand \cite{shneiderman1996}.
We follow the Visual Analytics mantra by analyzing first, show the important and analyze further \cite{Keim}.
%%
A first analysis step was performed by applying the classification algorithm to the data.
%%
The optimal classification uses a few rules to precisely characterize the target variable.
%%
Therefore, we are interested in \emph{small trees} with a \emph{low classification error}.
%%
The two measures form the axis for a \emph{scatter plot} of the classification results.

\paragraph{The Error Term. }
Normally the error for a classification is calculated with $error = \frac{classifiedCorrectly_{n}} {n}$ where $n$ is the number of subjects.
%%
The metric usually works well for variables with uniform distribution.
%%
It distorts the result for other distribution types.
%%
If for example a variable indicating a disease is negative for 90\% of the subjects and the classifier simply assigns all subjects to \emph{not ill} the error metric would yield an error of 10\%, even though it is very bad.
%%
Our error term therefore incorporates the discriminative power of each manifestation and is denoted as follows:
%%
%Therefore the discriminative power of each dimension in the equation
%error = 1 - \frac{\[ \sum_{m=0}^M \] \frac{M_{classifiedCorrectly}}{M_all}}{number of dimensions}
\begin{equation}
error = 1 - \frac{\sum_{m=0}^M \frac{classifiedCorrectly_{m}}{all_{m}}}{number_{dimensions}}
\end{equation}
$M$ represents the set of manifestation of each variable.
%%
The error is scaled to denote perfect classification with 0 and 1 is equal to random selection.
% The error rate has to be judged depending on the number of classes of the target variable.
% %%
% An error rate of 50\% for a target variable with two manifestations makes the classifier equal to throwing a coin.
% %%
% The same error rate is acceptable a target variable with more than two manifestations.
% %%
% Picking a value for a variable of four manifestations with an error rate of 50\% is better than the random selection (error rate of 75\%).
% %%
% The following scales the error rate so that 0 denotes perfect classification and 1 is equal to random selection.
% %%
% \begin{equation}
% error_{normalized} = \frac{error}{100 - \frac{100}{class number}}
% \end{equation}
%%
%%
We consider a result rated below $0.25$ a good classification.
%%
It allows for comparability of error rates between variables with different manifestation count.

@@

The x-axis shows the number of decisions of the underlying model, the y-axis the classification error (see Section~\ref{subsec:VisualizationOfClassificationResults}).

@@

We only display variables with an error below $0.5$, results above this threshold are inaccurate.

@@

\subsubsection{All Variables}
%%
The vast majority of parameters can not be described well using the classifier.
%%
This is reflected in the large amount of variables classified with an error above $0.6$.
%%
%The first impression of the resulting scatter plots quickly shows a very high amount of variables above an error rate of $0.6$.
%%

% None of the pain indicators can be reliably described using the image-based parameter.
None of the pain indicators can be described reliably using the image-based parameters.
%%
The only variable reliably classified in this group is gender. % with an error rate of 31.5\% using a decision tree of seven rules.
%
It can be discriminated with an error of $0.31$ using 7 rules and incorporates only curvature and curvature angle variables.
%%
The distinctness lies in the average difference in body size between male and female subjects.
%
%It mostly incorporates \emph{mean curvature}, \emph{sagittal curvature angle} und sagittal \emph{mean curvature}.
%The perfect categorization of the \emph{dialysis} parameter was conspicuous.
%%
%This is due to the subject distribution among the manifestation.
%%
%Only two subjects receive a dialysis.
%%
%The good discrimination is not meaningful.
%%
\emph{Medication for high blood pressure} is classified for 1,058 subjects with an error of $0.47$ solely based on coronal mean curvature.
%%
%1,058 subjects are classified with an error rate of $0,47$ solely based on coronal mean curvature.
%%
Almost all subjects who are medicated ($796/1,058$) were correctly classified, the vast majority of non-medicated subjects ($262/1,058$) are false-positive classified.
%%
Therefore the classifier is not as useful.
%%This is however due to the high amount of people, who are medicated (68\%) and who are almost all correctly class
%%
%Other features well classified include marital status, foot pain and number of born children.
%%
The four body size groups could be characterized with an error $0.48$, but the decision tree comprises 71 rules and imposes overfitting.

The analysis of the dummy variable yields similar results like the \emph{blood pressure medication}.
%%
Variables, such as subjects sized 139-164 cm, between 64 and 90 years of age or nutrition related parameters are dominantly populated by one manifestation.
%%
The classifier neglects the other group and yields a error below $0.5$.
%The dummy variable analysis yields fewer results.
%%
%It shows that subjects between 64 and 90 years of age can be detected with 23\% error rate by using the curvature angle and coronal mean curvature.
%%
%Subjects with body size between 177 cm and 202 cm can classified with an error rate of 22,1\%. solely using mean curvature.
%%
\subsubsection{Gender Groups}
%%
Classification using groups divided by gender do not produce satisfying results.
%%
Only \emph{hypothyroidism} could be described for male subjects with an error of $0.24$ for 110 subjects using the \emph{mean curvature} and \emph{curvature angle}.
%%
Since there are only 30 male subjects diagnosed with \emph{hypothyroidism}, the statistical power of the result is reduced.
%%
The dummy variable analysis showed that female subjects of \emph{139-164~cm body size} could be discriminated using the \emph{mean curvature} and \emph{curvature angle}, with an error of $0.38$.

%\com{Potentially skip these due to the confounding of body size}
\subsubsection{Body-Mass-Index Groups}
%%
Gender could be classified for each \emph{BMI} group using \emph{mean curvature} and \emph{curvature angle}.
%%
The error varies between $0.31$ (\emph{BMI} of \emph{$30.5-48$}, 4 decision rules) to $0.39$ (\emph{BMI} of \emph{$24.7-27.4$}, 5 decision rules).
%%
The starting age of smoking could be characterized well with an error between $0.25$ to $0.32$ for all \emph{BMI} groups except of subjects with BMI of \emph{$30.5-48$}.
%%
The result however is probably over fitted to the data due to tree sizes between $14$ and $16$.
%%
\com{Warum?}
%%

Some variables, such as \emph{body size} can be described with an error of $0.3$ to $0.36$ but only using large decision trees with over 20 rules.
%%
Notable is also the decreasing error with increasing decision tree size.
%%
Using mostly \emph{mean curvature} and \emph{curvature angle}, the leg pain level can be predicted using $14$ rules with an error of $0.46$ for obese subjects (\emph{BMI} higher than $30$).
%%
The dichotomous variable whether the subject has felt pain in the last seven days can also be predicted for this group using the same features.
%%
The resulting tree consists of $8$ rules and has an error of $0.35$.
%%
Obese subjects are prone to back and leg pain due to a more stressed lumbar spine.
%%
How much the spine is deformed under the heavy stress seems to directly influence the pain levels for these subjects.

The dummy variable analysis shows many results using a decision tree with one rule based on \emph{mean curvature} or \emph{curvature angle} with an error between $0.35$ and $0.47$.
%%
%It shows that mean curvature can be used to predict dependencies to variables, such as \emph{high blood pressure}, \emph{hypothyroidism} or \emph{nutrition}.

@@

\subsubsection{Size Groups}
%%
Many previously described results are confounded with subject size.
%%
Differences between \emph{male} and \emph{female} subjects are explained by to the average \emph{body size} difference.
%%
For example, large subjects are already characterized by their rather straight spine.
%
The question is, whether the inter-group spine-variability parameter is enough for predicting other parameter or not.
%%
Dividing subjects into \emph{body size} groups potentially highlights classifications not confounded by \emph{body size}.
%%
\paragraph{Large Decision Trees. }
Back pain-associated variables can be explained for various \emph{size}-groups, but we could not extract universal rules.
%%
Radiating back pain could be described with error of $0.39$ using 23 rules for subjects between \emph{$171-177~cm$ body size} using \emph{torsion} and \emph{mean curvature}.
%%
For subjects sized \emph{$177-202~cm$} the error increases to $0.47$ using 20 decision rules.
%%
There are several decision trees for laboratory values, such as \emph{alanine aminotransferase} value (relevant for diagnosis of liver or gallbladder illness) in the blood can be described with an error of $0.4$ (\emph{$139-164~cm$}) to $0.36$ (\emph{$164 - 171~cm$}).
%%
Similar values can be observed for \emph{cholesterol} or \emph{age}.
%%
Due to the large decision trees, these results are not usable and impose overfitting to the data.
%%
\paragraph{Small Decision Trees. }
%%
The dummy variables show several variables described using only one decision rule with an error between $0.42$ to $0.47$.
%%
Most of these variables have a dominant manifestation and the classifier shows a low detection precision for the second manifestation.
%%
These variables include \emph{nutrition} parameter, \emph{thyroid disorder} and \emph{social problems induced by back pain}.

@@

Subjects grouped using \underline{body size} have a similar spine shape and a lower variance.
%%
The remaining information within these groups is not enough to characterize back pain-related variables.
%%
For some \emph{body size} groups, certain \emph{nutrition} or \emph{psychological} parameters can be predicted with a comparatively high error.
%%

@@

\section*{\uppercase{Acknowledgements}}
\noindent Omitted due to blind review.
%\noindent SHIP is part of the Community Medicine Research net of the University of Greifswald, Germany, which is funded by the Federal Ministry of Education and Research (grant no. 03ZIK012), the Ministry of Cultural Affairs as well as the Social Ministry of the Federal State of Mecklenburg-West Pomerania. Whole-body MR imaging was supported by a joint grant from Siemens Healthcare, Erlangen, Germany and the Federal State of Mecklenburg-Vorpommern. The University of Greifswald is a member of the ‘Centre of Knowledge Interchange’ program of the Siemens AG. This work was supported by the DFG Priority Program 1335: Scalable Visual Analytics.
